\documentclass{article}

\usepackage{enumitem}
\usepackage{fontawesome}
\usepackage[margin = 0.5in, top=0.4in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{marvosym}
\usepackage{titlesec}
\usepackage{titling}
\usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}

%%%%%%%%%%%%%%%
% DEFINITIONS %
%%%%%%%%%%%%%%%

\definecolor{MyBlue1}{RGB}{28, 43, 112}
\definecolor{MyBlue2}{RGB}{35, 54, 140}
\definecolor{MyBlue3}{RGB}{42, 65, 168}

\newcommand{\smallbullet}{\,\begin{picture}(-1,1)(-1,-3)\circle*{3}\end{picture}\ }

\pagestyle{empty}
\setlength\columnsep{30pt}

\titleformat{\section}{\color{MyBlue2}\Large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\color{MyBlue1}\bfseries\large}{}{0em}{}
\titleformat{\subsubsection}[runin]{\bfseries}{}{0em}{}[:]

\titlespacing{\section}{0em}{0em}{0em}
\titlespacing{\subsection}{0em}{0em}{0.25em}
\titlespacing{\subsubsection}{0em}{0em}{0.25em}

\setlength{\leftmargini}{16pt}
\setlength{\parindent}{0pt}

\setlist{nolistsep}

\renewcommand{\maketitle}{
    \begin{center}
    {\color{MyBlue3}\Huge\bfseries
        \theauthor
    }

    \vspace{0.3em}
    {
        \href{mailto:arnav.kumar.sri@gmail.com}{\faEnvelope \ arnav.kumar.sri@gmail.com} \quad
        \href{https://github.com/arnavcs}{\faGithub \ arnavcs} \quad
        \href{https://arnavcs.github.io/}{\faGlobe \ arnavcs.github.io} \quad
        \href{https://www.linkedin.com/in/arnav-kumar-0644881a3/}{\faLinkedin \ Arnav Kumar}
    }
    \vspace{-1em}
    \end{center}
}

\newenvironment{resumeItem}
{
    \vspace{0.5em}
}
{
}

\newcommand{\projectHead}[3]{
    \textbf{#1} $\vert$ \textit{#2} \hfill #3 \\[-1.2em]
}

\newcommand{\achievement}[3]{
    #1, \textbf{#2} \dotfill #3 \\[-1.2em]
}

\newcommand{\experienceHead}[4]{
    \textbf{#1} @ #2 \hfill #3 \\[-1.2em]
}

\newenvironment{resumeList}
{
    \begin{itemize}[label=\smallbullet]
}
{
    \end{itemize}
}

%%%%%%%%%%%
% CONTENT %
%%%%%%%%%%%

\begin{document}

\title{R\'esum\'e}
\author{Arnav Kumar}

\maketitle

%% PROJECTS

\section{Projects}

\begin{resumeItem}
\projectHead{\href{https://github.com/arnavcs/cli-chess-engine}{CLI Chess Engine}}{Haskell}{Aug 2022 - Present}
\begin{resumeList}
    \item Implemented maybe monads to create safe functions for when there is nonsensical function application.
    \item Created custom haskell data types (such as a position data type) and ensured that no position could be created with had no meaning in the context of the board.
    \item Employed the use of applicative functors and monad operations on lists to write more concise code for tasks such as finding the cartesian product of two lists.
\end{resumeList}
\end{resumeItem}

\begin{resumeItem}
\projectHead{\href{https://github.com/arnavcs/arnavcs.github.io}{Modular Personal Website}}{Javascript, HTML, CSS}{Mar 2022 - Aug 2022}
\begin{resumeList}
    \item Built a simple content management system (CMS) with javascript which generates a DOM object from given data.
    \item Added several different section templates based on the type of information being conveyed.
\end{resumeList}
\end{resumeItem}

% \begin{resumeItem}
% \projectHead{\href{https://github.com/arnavcs/flashcards}{CLI Flashcards}}{Bash}{Apr 2022 - Apr 2022}
% \begin{resumeList}
%     \item Built a command line tool to add terms to, and practice with a flashcard set that the user can create.
%     \item Implemented several flag options, including a help option, version option, and script update option.
% \end{resumeList}
% \end{resumeItem}

\begin{resumeItem}
\projectHead{\href{https://github.com/arnavcs/ASCII-art}{Braille ASCII Art Generator}}{Python, OpenCV}{Apr 2021 - Jul 2021}
\begin{resumeList}
    \item Used OpenCV to manipulate and scale an input image and used thresholding to determine which cells of the output art should be colored.
    \item Translated the desired output image array into braille characters where every 2x3 block of cells was turned into a number corresponding to the desired ASCII braille character.
\end{resumeList}
\end{resumeItem}

\begin{resumeItem}
\projectHead{\href{https://github.com/arnavcs/OSIC-IPF}{Prognosing Idiopathic Pulmonary Fibrosis (IPF)}}{Python, Tensorflow2, Pandas, Scikit-learn}{Dec 2020 - Jun 2021}
\begin{resumeList}
    \item Predicted and gave a confidence value of the future lung volume of Idiopathic Pulmonary Fibrosis patients based on their initial lung capacity, and demographic (age, sex, smoking status, and more).
    \item Implemented an auto-encoder, linear regression, dense neural network, and bayesian model, which were able to accurately predict future lung capacity values with a standard deviation of approximately 200mL for the bayesian model.
    \item Obtained a Laplace Log Likelihood score of approximately -6.9, much better than the baseline score of -8.1.
\end{resumeList}
\end{resumeItem}

\begin{resumeItem}
\projectHead{\href{https://github.com/arnavcs/black-jack}{Blackjack}}{C++}{Apr 2021 - Jul 2021}
\begin{resumeList}
    \item Used object oriented programming to implement a blackjack game which the computer plays as the house.
    \item Sanitized user input and formatted output to be very readable, while displaying the player total.
\end{resumeList}
\end{resumeItem}

% \begin{resumeItem}
% \projectHead{\href{https://github.com/arnavcs/game-of-life}{Conway's Game of Life}}{Javascript}{Apr 2020 - Mar 2020}
% \begin{resumeList}
%     \item Created a javascript web version of Conway's Game of Life where a user chosen number of generations can be simulated.
%     \item Enabled the user to choose an initial arrangement of live and dead cells as well as the size of the initial grid.
% \end{resumeList}
% \end{resumeItem}
 
%% ACHIEVEMENTS

\section{Achievements}

\begin{resumeItem}
\begin{resumeList}
    \item \achievement{$10^{\mathrm{th}}$ in Canada}{Asian Pacific Mathematics Olympiad}{2022}
    \item \achievement{$11^{\mathrm{th}}$ in Canada}{Canadian Association of Physicists High School Exam}{2022}
    \item \achievement{2 time qualifier, $18^{\mathrm{th}}$ in Canada}{Canadian Mathematical Olympiad}{2021 - 2022}
    \item \achievement{Ranked $12^{\mathrm{th}}$ in Canada and $17^{\mathrm{th}}$ internationally}{Sir Isaac Newton Physics Exam}{2021 - 2022}
    \item \achievement{Invited to write}{United States of America Mathematical Olympiad}{2022}
    \item \achievement{Bronze medalist for project on Prognosing IPF}{Canada Wide Science Fair}{2021}
\end{resumeList}
\end{resumeItem}

    
%% EXPERIENCE

\section{Experience}

\begin{resumeItem}
\experienceHead{Part-time programmer}{Tektorch.ai}{Apr 2022 - Aug 2022}{Online}
\begin{resumeList}
    \item Created a web scraper for a jobs listing website using python, beatiful soup 4, numpy, and pandas to get features such as the job title, location, classification, and pay.
    \item Analysed and explored the nature of the data through data visualization using matplotlib, and regular expressions. 
    \item Created and learned the project design process by splitting tasks into managable, independant subtasks.
\end{resumeList}
\end{resumeItem}

% \begin{resumeItem}
% \experienceHead{Math competition teacher}{Webber Academy}{Aug 2021 - June 2022}{Calgary, AB.}
% \begin{resumeList}
%     \item Taught 4 children competition mathematics every week for 90 minutes after school.
% \end{resumeList}
% \end{resumeItem}

\begin{resumeItem}
\experienceHead{Part-time code sensei}{Code Ninjas West Springs}{Mar 2022 - Apr 2022}{Calgary, AB.}
\begin{resumeList}
    \item Worked with over 45 young students to help them complete programming challenges in scratch, makecode, and javascript.
    \item Summarized the progress of the students and reported to the manager.
\end{resumeList}
\end{resumeItem}

\begin{resumeItem}
\experienceHead{Computing Science High School Intern}{University of Alberta}{Jul 2021 - Aug 2021}{Online}
\begin{resumeList}
    \item Created graphs and animated GIFs of mouse position data during a psychology experiment using matplotlib.
    \item Used bash scripting to automate the creation of these graphs for all of the mouse data.
    \item Created natural language processing models based on word vectors to help determine the cause of a change in depressive language in Tweets.
\end{resumeList}
\end{resumeItem}

%% EDUCATION

\section{Education and Skills}

\begin{resumeItem}
\experienceHead{Bachelor of Computer Science}{University of Waterloo}{2022 - Present}{Waterloo, ON.}
\begin{resumeList}
    \item Recieved the Ronald G. Dunkley National Scholarship and the President's Entrance Scholarship of Distinction.
\end{resumeList}
\end{resumeItem}

% \begin{resumeItem}
% \experienceHead{International Summer School for Young Physicists (ISSYP)}{Perimeter Institute for Theoretical Physics}{Summer 2021}{Online}
% \end{resumeItem}

% \begin{resumeItem}
% \experienceHead{Quantum Cryptography School for Young Students (QCSYS)}{Institute for Quantum Computing, University of Waterloo}{Summer 2020}{Online}
% \end{resumeItem}

% \begin{resumeItem}
% \experienceHead{High School Diploma}{Webber Academy}{2008 - 2022}{Calgary, AB.}
% \begin{resumeList}
%     \item President of the Student Union and annual merit scholarship recipient.
% \end{resumeList}
% \end{resumeItem}

%% SKILLS 

% \section{Skills}

\begin{resumeItem}
\subsubsection{Languages}
Haskell, Python, C++, JavaScript, Java, Bash, {\LaTeX}, HTML, CSS, Markdown, Regex

\subsubsection{Libraries}
Pandas, Matplotlib, NumPy, Beautiful Soup, Tensorflow, Scikit-learn, OpenCV
\end{resumeItem}

\end{document}
